Storing messages with multipartite neural cliques

### 2014-07-16 Articles/article.tex
...

	\subsection{Simulations}
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $

	$\eta_\psi = max_x \, \eta_{x, \psi}$

@@

		Multipartite cliques don't improve theoretical efficiency (for not accepting messages that weren't previously seen by the network)

>>>>

	\subsection{Simulations}

	With random noise on edges, hardness of the problem must take into account the capacity of the binary symmetric channel (the closer $\psi$ is of $0.5$, the harder the problem is). Our new is efficiency is written as :  	
	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + \frac{1}{\log 2} \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $

	$\eta_\psi = max_x \, \eta_{x, \psi}$
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 units per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

@@

		Multipartite cliques don't improve theoretical asymptotic efficiency (for not accepting messages that weren't previously seen by the network).
